\documentclass[margin, line]{res}
\usepackage{enumitem}
\usepackage{changepage}
\usepackage{multicol}
\usepackage[most]{tcolorbox}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

% margins
%\topmargin=-0.5in
\oddsidemargin -1.5in
%\evensidemargin -1.5in
\textwidth=7.2in
%\itemsep=0in
%\parsep=0in
%\parskip=0in

% don't force fill to right and bottom
\raggedbottom
\raggedright

%-----------------------------------------------------------
% macros
\newenvironment{smitemize}{
  \begin{itemize}[nolistsep,noitemsep]
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
  }
  {\end{itemize}}

\newcommand{\resheading}[1]{
  \begin{tcolorbox}[width=\textwidth,
                    frame hidden,
                    colback=black!30,
                    enhanced,
                    top=0pt,
                    bottom=0pt,
                    height=16pt
                    ]
      \bf #1
  \end{tcolorbox}
  }

\newcommand{\ressubheading}[4]{
  \begin{minipage}{\textwidth}
  {\textbf{#1}\hfill #2} \\
  {\textit{#3}\hfill \textit{#4}}
  \end{minipage}
  \rule{\textwidth}{1pt}
  }

\newcommand{\projdescription}[2]{
  \begin{minipage}{\textwidth}
  \textbf{#1}
  \vspace{-2mm} \\
  \rule{\textwidth}{1pt}
  {#2}
  \end{minipage}
  }

\newcommand{\jobdescription}[5]{
  \begin{minipage}{\textwidth}
  \ressubheading{#1}{#2}{#3}{#4}
  \noindent{\textbf{Role:} #5}
  \end{minipage}
  }


%-----------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabbing}
  \textbf{\Large Joshua Reed} \` \textbf{\today} \\
  ReedJosh@oregonstate.edu    \` 3065 SW 178th Ave. \\
  (971) 275-5001              \` Beaverton, OR 97003 \\ 
\end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Objective}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To obtain a full time design or test engineering position 
which requires creativity and encourages self advancement. An ideal position might 
include low level programming, scripting for productivity and  hardware or 
system design or test.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ressubheading{Oregon State University}
              {Corvallis, OR}
              {B.Sc. Electrical and Computer Engineering}
              {2012 - Graduating: June, 2017}
\begin{itemize}[nolistsep, noitemsep, topsep=0pt]
  \item{\bf GPA 3.5}
  \item{\bf Focus in Computer Engineering and Digital Design} 
  \item Key Courses Include:
    \setlength{\multicolsep}{0pt}
    \begin{multicols}{2}    
      \begin{itemize}[nolistsep,noitemsep,topsep=0pt]
        \item Digital Logic Design  
        \item Assembly Language 
        \item Algorithms 
        \item Microcontroller System Design 
        \item Operating Systems 
        \item VLSI and VLSI System Design 
        \item Computer Architecture 
      \end{itemize}
    \end{multicols}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\begin{adjustwidth}{-10pt}{0pt} 
  \setlength{\multicolsep}{0pt}
  \begin{multicols}{2}    
    \begin{itemize}[nolistsep, noitemsep, topsep=0pt]
      \item {\bf HDL:} VHDL, Verilog, Modelsim and ActiveHDL Simulators and Altera Quartus II Design Software
      \item {\bf System Design:} Microcontrollers, FPGAs and Basic Communication Protocols
      \item {\bf Development \& Productivity Tools:} Microsoft Office Suite, Vim, Latex and Git
      \item {\bf Software Design:} Object Oriented Programming, Linux System  
                                   Interaction, Regular Expressions, C and Python
      \item {\bf Hardware Design:} Discrete Logic Design, Transistor Layout Basics, 
                                   Circuit Design, PCB Layout and Power Supply Concepts
    \end{itemize}
  \end{multicols}
\end{adjustwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Internship and Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\jobdescription{Mentor Graphics}
               {Wilsonville, OR}
               {Technical Marketing Engineer Intern}
               {July, 2016 - Current}
               {As a Technical Marketing Engineer Intern I participated in team meetings 
and gave occasional presentations. My primary focus was a regression testing program that 
converted arbitrary graphs to usable input for Mentor's 
Calibre tools. Mostly written in Python, this project parsed graph files, generated SVRF and TVF
scripts and managed process control of external programs. Designed for use in a Linux
environment, I gained experience interacting with Linux development tools and 
the operating system itself.} % rewrite to what I did
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\jobdescription{Oregon State University}
               {Corvallis, OR}
               {Digital Design Lab TA}
               {March, 2014 - January, 2015 \& September, 2015 - July 2016} % dates
               {As a teaching assistant I worked directly with instructor 
Matt Shuman to help guide the lab 
portion of the course. On occasion I developed and lead class lectures,
managed lab grading and built lab study material. One of
the larger projects I developed for the course was an FPGA voltmeter which required
implementation of a SPI communications protocol.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\jobdescription{Garmin AT}
              {Salem, OR}
              {Design Engineer Intern}
              {March - September, 2015}
{As a Design Engineer Intern at Garmin AT I interacted with a team of 
four and my team lead on a daily basis. Primarily I worked to redesign a 
portion of an aerial receiver's HDL that targeted an Altera FPGA. The main goal of
this redesign was to reduce logic utilization. I achieved a reduction of $60\%$ 
while also implementing VHDL 2008 constructs to develop cleaner, more extensible code. 
Other projects included parsing CSV Oscilloscope readings of USB communications, 
generating a top down compilation order for a large VHDL project using Python 
and developing a discrete % 
logic circuit to multiplex LCD display data. During this internship I gained experience 
with a larger VHDL project, circuit design and layout, power
supply design, Visual Basic, Python and Batch scripting and electronics lab tool usage.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\jobdescription{Riverstone Residential}
               {Portland, OR}
               {Maintenance Supervisor}
               {July, 2009 - September, 2012}
{As a Maintenance Supervisor at Riverstone Residential I managed a team 
of three people toward the goal of maintaining 
over 350 homes located within a 10 mile radius. My responsibilities included: ordering
supplies, scheduling of both vendors and employees, maintenance repair requests and 
resident communication. While in this position I developed skills in problem 
solving, communication, time management and leadership.}

\resheading{Project and Extracurricular Experience}

\projdescription{VLSI System Design}
                {I worked with instructor Roger Traylor to integrate FPGAs into OSU's 
VLSI System Design course. This included preparing and delivering two demonstrative 
lectures, building course assignments and exploring design options. During this process, I
designed a blinking led pll demo and a sine wave generator which utilized the 
FPGA's on chip rom.}

\projdescription{Senior Design High Field Pulse Magnet}
                {Our project met or exceeded initial requirements. I helped
achieve this goal by designing a voltmeter and voltage warning indicator. For the 
final prototype I successfully designed and utilized a PCB.}

\projdescription{More Power Amplifier Design}
                {I implemented a bridged amplifier design to improve upon a USB powered 
discrete transistor amplifier. To do this I added a unity gain stage to one half of the 
amplifier, inverting the phase of the original signal.}

\resheading{References}

    \ressubheading{Marshal Barrett}
                  {{(541) 908-6761} -- MarshalBarrett@gmail.com}
                  {Senior Design Engineer}
                  {Garmin AT}

    \ressubheading{Chris Schulte}
                  {(503) 391-3303 -- Chris.Schulte@garmin.com}
                  {Staff Engineer}
                  {Garmin AT}

    \ressubheading{Matthew Shuman}
                  {(541) 737-1072 -- ShumanM@oregonstate.edu}
                  {Instructor}
                  {Oregon State University} 

    \ressubheading{Roger Traylor}
                  {(541) 737-2975 -- Traylor@eecs.oregonstate.edu}
                  {Senior Instructor}
                  {Oregon State University}

    \ressubheading{Lisa Shoop}
                  {(503) 998-4266 -- {\it Please Call}}
                  {Regional Manager}
                  {Riverstone Residential}
\end{document}

